Comparing MTurk and the US Population's Occupational Diversity

### 2018-09-17 Manuscript.Rmd
Updated local.

```{r,BLS, include=FALSE, results='asis'}
#Load packages
library(readr)
library(readxl)
library(data.table)
library(openxlsx)

@@

# Download the file with download.file()
# Here is the URL.
download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
unzip("BLS2015.zip")
library(readxl)
national_M2015_dl <- read_excel("oesm15nat/national_M2015_dl.xlsx")
View(national_M2015_dl)

#Edit the code below such that the newly downloaded data aligns with the code below. You'll need to include relative percentages.

BLS <- read_excel("~/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/BLS Data from 2015.xlsx")
###Rename rows and aggregate.
BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
BLS[11, 1] = "31-39 Service Occupations"
BLS[12, 1] = "31-39 Service Occupations"
BLS[13, 1] = "31-39 Service Occupations"
BLS[14, 1] = "31-39 Service Occupations"
BLS[15, 1] = "31-39 Service Occupations"
BLS[16, 1] = "41 Sales and Related Occupations"
BLS[17, 1] = "43 Office and Administrative Support Occupations"
BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
BLS[19, 1] = "47 Construction and Extraction Occupation"
BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
BLS[21, 1] = "51 Production Occupation"
BLS[22, 1] = "53 Transportation and Material Moving Occupation"
BLS[23, 1] = "55 Military Specific Occupations"
names(BLS) <- c("Var1","Var2","Var3")
BLS <- aggregate(.~Var1,BLS,sum)
###Data on the size of the military taken from the department of defense (http://us-military-branches.insidegov.com). 
BLS[13, 2] = "1350236"
names(BLS) <- c("Intermediate Aggregation Title", "Freq","RFreq")
BLS$Freq <- as.numeric(BLS$Freq)
tab <- transform(BLS, relative = prop.table(Freq))
BLS <- tab[c(1,4)]
names(BLS) <- c("Intermediate Aggregation Title","e")
```

```{r Sample Data, include=FALSE, results='asis', echo=FALSE}
##LATech data
LATech <- read_csv("/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/Chris's Data from 2015.csv")
###Delete unneeded data.
LATech <- LATech[c(1:3)]
###Edit data. Some participants provided incorrect codes or no codes.
LATech[703, 3] = "43-6011.00"
LATech[704, 3] = "43-6011.00"
LATech[705, 3] = "43-6011.00"
LATech[706, 3] = "43-6011.00"
LATech[707, 3] = "43-6011.00"
LATech[755, 3] = "43-9199.00"
LATech[756, 3] = "11-3051.01"
LATech[757, 3] = "43-3031.00"
LATech[758, 3] = "17-2199.00"
LATech[759, 3] = "13-2099.00"
LATech[760, 3] = "33-3051.01"
LATech[761, 3] = "23-1011.00"
LATech[762, 3] = "27-3099.00"
LATech[763, 3] = "17-2199.00"
LATech[765, 3] = "43-9061.00"
LATech[766, 3] = "39-5012.00"
LATech[768, 3] = "19-4061.00"
LATech[769, 3] = "41-4011.00"
LATech[770, 3] = "43-4171.00"
LATech[771, 3] = "15-1134.00"
LATech[772, 3] = "37-2012.00"
LATech[773, 3] = "41-1011.00"
LATech[775, 3] = "25-0000.00"
LATech[776, 3] = "25-0000.00"
LATech[779, 3] = "13-1111.00"
LATech[781, 3] = "29-1171.00"
LATech[782, 3] = "37-2012.00"
LATech[785, 3] = "35-2014.00"
LATech[786, 3] = "29-1123.00"
LATech[784, 3] = "25-0000.00"
###Remove unemployed cases.
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
LATech <- completeFun(LATech, "O*NET Job Code")

###Abbreviate data, consolidate into intermediate categories, and bind.
LO <- LATech[c(3)]
LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
names(LO) <- c("Int.Agg.Cat")
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
LATech <- cbind(LATech,LO)
###Build relative frequency table.
tab <- as.data.frame(table(LATech$Int.Agg.Cat, exclude=NULL))
tab <- transform(tab, relative = prop.table(Freq))
names(tab) <- c("Intermediate Aggregation Title","n","f")
#Table for poster.
table <- merge(BLS,tab, by="Intermediate Aggregation Title", all=TRUE)

@@

UGA <- read_excel("/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/Rachel's Data from 2015.xlsx")

>>>>

```{r Load Data, include=FALSE, results='asis'}
#Load packages
library(readr)
library(readxl)
library(data.table)
library(openxlsx)

@@

# Download the file with download.file()
# Here is the URL.
download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
unzip("BLS2015.zip")
library(readxl)
BLS <- read_excel("oesm15nat/national_M2015_dl.xlsx")
BLS <- BLS[c(2,4)]

# Include data on the size of the military (taken from the department of defense (http://us-military-branches.insidegov.com))
BLS <- rbind(BLS, c("Military Specific Occupations", 1350236))

#Only keep intermediate category totals.
BLS <- BLS[c(2,71,129,162,222,293,320,336,432,494,586,612,653,687,705,767,810,923,950,1054,1130,1298,1395,1),]

###Rename rows and aggregate.
BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
BLS[11, 1] = "31-39 Service Occupations"
BLS[12, 1] = "31-39 Service Occupations"
BLS[13, 1] = "31-39 Service Occupations"
BLS[14, 1] = "31-39 Service Occupations"
BLS[15, 1] = "31-39 Service Occupations"
BLS[16, 1] = "41 Sales and Related Occupations"
BLS[17, 1] = "43 Office and Administrative Support Occupations"
BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
BLS[19, 1] = "47 Construction and Extraction Occupation"
BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
BLS[21, 1] = "51 Production Occupation"
BLS[22, 1] = "53 Transportation and Material Moving Occupation"
BLS[23, 1] = "55 Military Specific Occupations"
names(BLS) <- c("Var1","Var2")
BLS$Var2 <- as.numeric(BLS$Var2)
BLS <- aggregate(.~Var1,BLS,sum)

#Add military occupation number to the overall. 
BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]

#Rename variables
names(BLS) <- c("Intermediate Aggregation Title", "Freq")

#Only keep occupational categories (no all).
BLS <- BLS[-14,]

#Compute relative frequencies. Call the object "tab".
tab <- transform(BLS, relative = prop.table(Freq))

#Define new BLS. "e" is for "relative frequency". 
BLS <- tab[c(1,3)]
names(BLS) <- c("Intermediate Aggregation Title","e")

##LATech data
LATech <- read_csv("Data/Chris's Data from 2015.csv")
###Delete unneeded data.
LATech <- LATech[c(1:3)]
###Edit data. Some participants provided incorrect codes or no codes.
LATech[703, 3] = "43-6011.00"
LATech[704, 3] = "43-6011.00"
LATech[705, 3] = "43-6011.00"
LATech[706, 3] = "43-6011.00"
LATech[707, 3] = "43-6011.00"
LATech[755, 3] = "43-9199.00"
LATech[756, 3] = "11-3051.01"
LATech[757, 3] = "43-3031.00"
LATech[758, 3] = "17-2199.00"
LATech[759, 3] = "13-2099.00"
LATech[760, 3] = "33-3051.01"
LATech[761, 3] = "23-1011.00"
LATech[762, 3] = "27-3099.00"
LATech[763, 3] = "17-2199.00"
LATech[765, 3] = "43-9061.00"
LATech[766, 3] = "39-5012.00"
LATech[768, 3] = "19-4061.00"
LATech[769, 3] = "41-4011.00"
LATech[770, 3] = "43-4171.00"
LATech[771, 3] = "15-1134.00"
LATech[772, 3] = "37-2012.00"
LATech[773, 3] = "41-1011.00"
LATech[775, 3] = "25-0000.00"
LATech[776, 3] = "25-0000.00"
LATech[779, 3] = "13-1111.00"
LATech[781, 3] = "29-1171.00"
LATech[782, 3] = "37-2012.00"
LATech[785, 3] = "35-2014.00"
LATech[786, 3] = "29-1123.00"
LATech[784, 3] = "25-0000.00"

###Remove unemployed cases.
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

LATech <- completeFun(LATech, "O*NET Job Code")

###Abbreviate data, consolidate into intermediate categories, and bind.
LO <- LATech[c(3)]
LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
names(LO) <- c("Int.Agg.Cat")
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
LATech <- cbind(LATech,LO)

###Build relative frequency table.
tab <- as.data.frame(table(LATech$Int.Agg.Cat, exclude=NULL))
tab <- transform(tab, relative = prop.table(Freq))
names(tab) <- c("Intermediate Aggregation Title","n","f")

#Table for poster.
table <- merge(BLS,tab, by="Intermediate Aggregation Title", all=TRUE)

@@

UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
